\documentclass[12pt,a4paper]{book}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage[italian]{babel}
\usepackage{fixltx2e,bold-extra,geometry,
    amssymb,amsmath,mathtools, microtype,url,cite}
\usepackage[bookmarks=true, hidelinks, pdftitle={
RELAZIONE FINALE SISTEMI DIGITALI M},
pdfauthor={De Nardi-Tornatore}]{hyperref}
% \pagestyle{headings}
\graphicspath{{images/}}

\usepackage{float} %use H in pictures

\usepackage{pgfplots}

% Default fixed font does not support bold face
\DeclareFixedFont{\ttb}{T1}{txtt}{bx}{n}{9} % for bold
\DeclareFixedFont{\ttm}{T1}{txtt}{m}{n}{9} % for normal

% Custom colors
\usepackage{color}
\definecolor{deepblue}{rgb}{0.45,0.95,0.36}
\definecolor{deepred}{rgb}{0,0,0}
\definecolor{deepgreen}{rgb}{0.67,0.31,0.31}
\definecolor{deepblack}{rgb}{0.11,0.11,0.11}
\definecolor{lightblue}{rgb}{0.77, 0.89, 0.93}

\usepackage{listings}

% Python style for highlighting
\newcommand\pythonstyle{\lstset{
		backgroundcolor=\color{deepblack},
		language=Python,
		basicstyle=\ttm\color{white},
		morekeywords={self},              % Add keywords here
		keywordstyle=\ttb\color{deepblue},
		emph={MyClass,__init__},          % Custom highlighting
		emphstyle=\ttb\color{deepred},    % Custom highlighting style
		stringstyle=\color{deepgreen},
		commentstyle=\ttm\color{lightblue},
		frame=tb,                         % Any extra options here
		showstringspaces=false
}}


% Python environment
\lstnewenvironment{python}[1][]
{
	\pythonstyle
	\lstset{#1}
}
{}

% Python for external files
\newcommand\pythonexternal[2][]{{
		\pythonstyle
		\lstinputlisting[#1]{#2}}}

% Python for inline
\newcommand\pythoninline[1]{{\pythonstyle\lstinline!#1!}}


%%%%%%%%%%%%%%%%% New Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\newcommand{\intentblankpage}{
%     Leaves a blank page
    \newpage
    \null
    \vfill
    \thispagestyle{empty}
    \begin{center}
%         \textit{This page intentionally left blank.}
        \textit{Questa pagina \`e lasciata intenzionalmente bianca.}
    \end{center}
    \newpage
}
% 
% Writes intentionally blank page when there is a \newpage on the left page of
% a book.
\makeatletter
    \def\cleardoublepage{\clearpage%
        \if@twoside
            \ifodd\c@page\else
                \vspace*{\fill}
                \hfill
                \begin{center}
%                     \textit{This page intentionally left blank.}
                    \textit{}
                \end{center}
                \thispagestyle{empty}
                \newpage
                \if@twocolumn\hbox{}\newpage\fi
            \fi
        \fi
    }
\makeatother
%
% Length to set margins for 65 chars
\newlength{\sixtyfivecharwidth}
\settowidth{\sixtyfivecharwidth}{
    \normalfont abcdefghijklmnopqrstuvwxyzabcdefghijklmnopqrstuvwxyz1234567890123}
% 
%Integral with the limit below(mathrlap)
% \newcommand{\intlimr}[1]{\ensuremath{\int \limits_{\mathrlap{#1}}}}
% 
% This redefine could cause big issues! See: 
% http://tex.stackexchange.com/questions/248421/use-mathclap-as-default-in-limits-of-integration
% \let\oldlimits\limits
% \def\limits_#1{\oldlimits_{\mathclap{#1}}}
\def\mclimits_#1{\limits_{\mathclap{#1}}}
%%%%%%%%%%%%%%%% End New Commands %%%%%%%%%%%%

\begin{document}
    \pagenumbering{Roman}
    \input{./titlepage}
    
    \tableofcontents
    
    \chapter*{Introduzione} \pagenumbering{arabic}
    \addcontentsline{toc}{chapter}{Introduzione}
    \label{CH:Intro}
    \input{./introduzione}
    
    \chapter{Chitarra}
    \label{CH:Teoria}
    \input{./capI}
    
    \chapter{Trasformata a Q Costante}
    \label{CH:Teoria}
    \input{./capII}
    
    \chapter{Architettura e addestramento del modello}
    \label{CH:Val_num}
    \input{./capIII}
    
    \chapter{Implementazione su dispositivo Embedded}
    \label{CH:Val_num}
    \input{./capIV}
    
    \chapter{Conclusioni}
    \label{CH:Concl}
    \input{./conclusioni}
    
%     \nocite{*}
    \bibliographystyle{IEEEtran}
    %%%%%%%%%%% Example 1%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{thebibliography}{100}  % 100 is a random guess of the total number of %references
    
    \bibitem{HK} \textit{Chitarra classica}. (s.d.). Wikipedia, l'enciclopedia libera. Ultimo accesso: 28 febbraio 2021, https://it.wikipedia.org/wiki/Chitarra
    
    \bibitem{HK} \textit{I tasti della chitarra}. (s.d.). TestoeAccordi. Ultimo accesso: 26 febbraio 2021, https://www.testoeaccordi.it/menu/tasti.htm
    
    \bibitem{HK} \textit{Note manico chitarra} [Image]. (s.d.). Videocorsochitarra. Ultimo accesso: 27 febbraio 2021, https://videocorsochitarra.it/note-manico-chitarra/
    
    \bibitem{HK} Savage. N. (s.d.). \textit{Come Leggere Tablature per Chitarra}. Wikihow. https://www.wikihow.it/Leggere-Tablature-per-Chitarra
    	
    \bibitem{Boney96} Q. Xi, R. Bittner, J. Pauwels, X. Ye, and J. P. Bello, "Guitarset: A Dataset for Guitar Transcription", \emph{in 19th International Society for Music Information Retrieval Conference}, Paris, France, Sept. 2018.
    
    \bibitem{MG} Note Frequency Chart (Download) [Image], Soundonsound.com, Dec 03, 2018 11:32 am.
    
    \bibitem{HK} Drexel University, ExCITe Center, \emph{Expressive and Creative Interaction Technologies}, NEMISIG 2019
    
    \bibitem{HK} \textit{Utilizza un modello TensorFlow Lite per inferenza con ML Kit su iOS}. (s.d.). Firebase. Ultimo accesso: 03 marzo 2021, https://firebase.google.com/docs/ml-kit/ios/use-custom-models

	\end{thebibliography}
	%%%%%%%%%%%%% end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
